---
title: "Analysis of Rental Housing Market"
author: 'Fiseha Amine,Martina Schüpbach-Wolf  '
date: "02 02 2021"
output:
  pdf_document: default
  html_document: default
---

\newpage 
\tableofcontents
\listoffigures
\listoftables
\newpage



#######################
--> Questions:

- Sind die gekürzen Namen ok?
- Wollen wir vor die neuen Spalten jeweils "neu_" schreiben?
- Die Ziele (unten) können wir ja noch anpassen...
- Als Erinnerung: Datum am Schluss der Arbeit noch anpassen
- Brauchen wir listof figures - tables als Verzeichnis (oben)?
- verwenden wir für die Namensbezeichnung der Datensätze einen ". oder _"?
- ich habe in dem dazugefügten Datensatz in der Exceltabelle Namen angepasst. Ich weiss das ist nicht gut, aber meinst du es ist ok? Ansonsten versuche ich es hier im File, was wahrscheinlich "sauberer" wäre.


#######################


# Introduction
This project analysis is part of the R-Bootcamp module from HS 2020.
It contains the topics that have been covered in the module.

# Aim of Analysis
The aim to analyze the rental housing market in Switzerland with open access data from 2019.

Our goals are to:
- analyze the price in relation to geography and per canton
- show where are most apartments
- show where are the most expensive apartments (canton/community)
- show where are the biggest apartments
- show what kind of apartments are most
- Is there a relation ship of the number of people in the canton and size of appartments?


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r, message=FALSE}
library(readxl)
library(tidyverse)
library(dplyr)
library(mlbench)
library(mice)
library(ggplot2)
library(plotly)
```

# Data Import


# Data Import
The data set was downloaded from "Datenportal Schweiz_Wohungsmieten": <https://datenportal.info/wohnungsmarkt/wohnungsmieten/>

It contains the following attributes (in German): 
  ID, Year, Quarter, Apartment type, Room, Area, Rent Gross, Square Meter, Price Gross, Address, Postcode and City, Move-In Date,        Building Coordinates, Canton

```{r}
#Because the data contain "Umlaute" we use "UTF-8" for the read in.
data <- read.csv2("mietinserate_v1.csv", header = TRUE, fileEncoding = "UTF-8")
head(data)
str(data)
summary(data)
```


# Data Preparation
For the upcoming analysis the data needs to get formatted and cleaned.We transform the data into a data frame. We also transform numeric data into numeric and transform the date data into the correct format.we also rename column names for better readability.
```{r}

data <- as.data.frame(data)

data$Zimmer = as.numeric(data$Zimmer)
data$Fläche = as.numeric(data$Fläche)
data[data == ""] <- NA
data$Bezugsdatum =as.Date(data$Bezugsdatum, "%d.%m.%Y")
data.1 <- rename(data, W.Type = Wohnungstyp, Miete = Mietpreis_Brutto, Quad_m = Quadratmeterpreis_Brutto, Bezug = Bezugsdatum, W.Fläche = Fläche)
data.1
```

## Missing values

Here all missing data get shown in a plot to get an overview of the distribution of them.
Also we can observe how many cantons have how many NAs in relation to...

```{r, MissingValues, echo=FALSE, fig.height = 10, fig.width = 17}
colSums(is.na(data.1)) ##counts all NA in a table
md.pattern(data.1, rotate.names = TRUE) ##shows a table and a plot of the data for the NAs

# data_kanton <- group_by(data, "KT")
# sum(is.na(data_kanton$Fläche))

data.1 %>% count(KT, sort = TRUE) #shows the amount of cantons in dataset per canton

data.1 %>%
  group_by(KT) %>% 
  summarise(non_na_count = sum(is.na(Zimmer))) #Lists all cantons and shows the "NAs"
  
data.1 %>%
     filter(is.na(Zimmer))  %>%
      count(KT) #Shows on the found cantons with NAs

```

## Data Modification

In this step we split the column "PLZ_Ort" which consists a postal code and city name to PLZ and Ort. 

```{r}
data_sep <- data.1$PLZ_Ort%>%
  str_match('(.*\\d) (.*)') %>%
  as_tibble() %>%
  select(2:3) %>%
  set_names(c('PLZ', 'Ort'))
data_sep
```

As this columns are saved separately from the main dataset, we merge it again to the main dataset and remove the old column "PLZ_Ort".

```{r}
data_sort <- data.1%>%select(-PLZ_Ort)
data_clean <- bind_cols(data_sort, data_sep)
data_clean

# data_sort <- data_sort%>%select(-PLZ_Ort)
# data_clean <- bind_cols(data_sort, data_sep)
# data_clean
```

## Add new data set

To also have an overview of the number of residents in the canton, we add a new data set.
We extracted the data set from: <https://www.citypopulation.de/de/switzerland/cities/>

```{r}
#Read new data set and join new data set to our data set.
data_canton <- read_xlsx("SchweizKantone_Einwohner.xlsx", skip = 3)
head(data_canton)
str(data_canton)

#prepare for the join
data_canton <- rename(data_canton, KT = Kanton, CH = Schweiz, G.Fläche = Gemeindefläche)

data_left_join <- left_join(data_clean, data_canton, by = "KT")
head(data_left_join)
data_left_join
```


# Graphical Analysis

```{r}
head(data_left_join)
str(data_left_join)

```
## Graphical Visualisation

```{r}
plot(y = data_left_join$Miete,
     x = data_left_join$W.Fläche,
     pch = "x",
     title("Price per appartment"),
           xlab = "living space",
           ylab = "rent")
#abline()

ggplot(data_left_join, aes(x=Miete, y=W.Fläche) ) +
  geom_hex(bons = 70) +
  scale_fill_continuous(type = "viridis") +
  theme_bw()
```

##Plotversuche
```{r}

ggplot(data_left_join, aes(x=Miete, y=Zimmer, color=W.Type))+
  geom_point(size=2)

##

qplot(y = Zimmer, x = Miete, data = data_left_join, facets = ~ W.Type)

##

boxplot(Zimmer ~ W.Type, data = data_left_join, main = "xxx")

##

fig <- plot_ly(data = data_left_join, x = ~Einwohner_2019, y = ~G.Fläche,
               marker = list(size = 10,
                             color = 'rgba(255, 182, 193, .9)',
                             line = list(color = 'rgba(152, 0, 0, .8)',
                                         width = 2)))
fig <- fig %>% layout(title = 'Styled Scatter',
         yaxis = list(zeroline = FALSE),
         xaxis = list(zeroline = FALSE))

fig

##
###hier gerne plot mit "wenn Miete teurer ist, dann andere Farbe"
fig <- plot_ly(data_left_join, x = ~KT, y = ~Miete, type = 'bar', color = I("black"))
fig <- fig %>% layout(title = "Rent per canton",
         xaxis = list(title = ""),
         yaxis = list(title = ""))

fig

# fig <- plot_ly(data_left_join, x = ~KT, y = ~Miete, type = 'bar', color = ifelse("Miete" > 3000,'green'))
# fig <- fig %>% layout(title = "Rent per canton",
#          xaxis = list(title = ""),
#          yaxis = list(title = ""))
# 
# fig



```


## Corellation matrix
```{r}
pairs(~Zimmer+Miete+W.Fläche+G.Fläche+Einwohner_2019,data=data_left_join,
      main="Simple Scatterplot")

```


# Analysis

```{r}
data_left_join%>%
top_n(n = 10, wt = Miete)
```

