---
title: "Analysis of Rental Housing Market"
author: "Fiseha Amine,Martina Schüpbach-Wolf  "
date: "2 2 2021"
output: html_document
---

/ Break page
/Table of Contents


#######################
--> Questions:
- Sollten wir auch den Mietpreis umwandeln?
- Sind die gekürzen Namen ok?
- "Wohnungstyp" hat 18 leere Zellen ("Seite: 25). Es wird nicht gezeigt. Warum?


#######################


# Introduction
This project analysis is part of the R-Bootcamp from HS 2020.
It contains the topics that have been covered in the module.

# Aim of Analysis
The aim to analyze the rental housing market in Switzerland with open access data from 2019.

Our goals are to:
- analyze the price in relation to geography and per canton
- show where are most apartments
- show where are the most expensive apartments (canton/community)
- show where are the biggest apartments
- show what kind of apartments are most


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Libraries
```{r}
library(tidyverse)
library(dplyr)
library(mice)
```


# Data Import
The data set was downloaded from "Datenportal Schweiz_Wohungsmieten": <https://datenportal.info/wohnungsmarkt/wohnungsmieten/>

It contains following data (in German): 
  ID, Year, Quarter, Apartment type, Room, Area, Rent Gross, Square Meter, Price Gross, Address, Postcode and City, Move-In Date,        Building Coordinates, Canton

```{r}
#Because the data has "Umlaute" we use "UTF-8" for the read in.
data <- read.csv2("mietinserate_v1.csv", header = TRUE, fileEncoding = "UTF-8")
head(data)
str(data)
```


# Data Preparation
```{r}
#We transform the data into a data frame and also transform numeric data into numeric and transform the date data into the correct format.
data <- as.data.frame(data)

data$Zimmer = as.numeric(data$Zimmer)
data$Fläche = as.numeric(data$Fläche)
data$Bezugsdatum =as.Date(data$Bezugsdatum, "%d.%m.%Y")
str(data)
```

```{r}
#shorten column names
data.1 <- rename(data, W.Type = Wohnungstyp, Miete = Mietpreis_Brutto, Quad_m = Quadratmeterpreis_Brutto, Bezug = Bezugsdatum)
data.1

```


## Missing values

```{r, MissingValues, echo=FALSE, fig.height = 9, fig.width = 16}
colSums(is.na(data.1)) ##counts all NA
md.pattern(data.1, rotate.names = TRUE) ##shows a table and a plot of the data for the NAs




sum(is.na(data$W.Typ))
# 
# data_kanton <- group_by(data, "KT")
# sum(is.na(data_kanton$Fläche))
```

## Data Modification

```{r}
data$PLZ_Ort %>%
  str_match('(.*\\d) (.*)') %>%
  as_tibble() %>%
  select(2:3) %>%
  set_names(c('PLZ', 'Ort'))
```


# Graphical Analysis

```{r}
head(data)
str(data)
```
## Graphical Visualisation

```{r}
plot(y = data$Mietpreis_Brutto,
     x = data$Fläche,
     pch = "x", "preis pro Wohnung")
```

## Corellation's matrix


# Analysis

```{r}
data%>%
top_n(n = 10, wt = Mietpreis_Brutto)
```

