---
title: "Analysis of Rental Housing Market"
author: 'Fiseha Amine,Martina Schüpbach-Wolf  '
date: "02 02 2021"
output:
  pdf_document: default
  html_document: default
---

\newpage 
\tableofcontents
\listoffigures
\listoftables
\newpage



#######################
--> Questions:
- Sollten wir auch den Mietpreise umwandeln und die Kantone als Factor?
- Sind die gekürzen Namen ok?
- Wollen wir vor die neuen Spalten jeweils "neu_" schreiben?
- Die Ziele können wir ja noch anpassen.
- Datum am Schluss der Arbeit noch anpassen
- Brauchen wir listof figures - tables?
- verwenden wir für die Namensbezeichnung der Datensätze einen ". oder _"?
- ich habe in dem dazugefügten Datensatz in der Exceltabelle Namen angepasst. Ich weiss das ist nicht gut, aber meinst du es ist ok?


#######################


# Introduction
This project analysis is part of the R-Bootcamp module from HS 2020.
It contains the topics that have been covered in the module.

# Aim of Analysis
The aim to analyze the rental housing market in Switzerland with open access data from 2019.

Our goals are to:
- analyze the price in relation to geography and per canton
- show where are most apartments
- show where are the most expensive apartments (canton/community)
- show where are the biggest apartments
- show what kind of apartments are most
- Is there a relation ship of the number of people in the canton and size of appartments?


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r, message=FALSE}
library(readxl)
library(tidyverse)
library(dplyr)
library(mlbench)
library(mice)
```

# Data Import


# Data Import
The data set was downloaded from "Datenportal Schweiz_Wohungsmieten": <https://datenportal.info/wohnungsmarkt/wohnungsmieten/>

It contains following data (in German): 
  ID, Year, Quarter, Apartment type, Room, Area, Rent Gross, Square Meter, Price Gross, Address, Postcode and City, Move-In Date,        Building Coordinates, Canton

```{r}
#Because the data contain "Umlaute" we use "UTF-8" for the read in.
data <- read.csv2("mietinserate_v1.csv", header = TRUE, fileEncoding = "UTF-8")
head(data)
str(data)
summary(data)
```


# Data Preparation
For the upcoming analysis the data needs to get formatted and cleaned.
```{r}
#We transform the data into a data frame. We also transform numeric data into numeric and transform the date data into the correct format.
data <- as.data.frame(data)

data$Zimmer = as.numeric(data$Zimmer)
data$Fläche = as.numeric(data$Fläche)
data[data == ""] <- NA
data$Bezugsdatum =as.Date(data$Bezugsdatum, "%d.%m.%Y")
```


```{r}
#shorten column names
data.1 <- rename(data, W.Type = Wohnungstyp, Miete = Mietpreis_Brutto, Quad_m = Quadratmeterpreis_Brutto, Bezug = Bezugsdatum, W.Fläche = Fläche)
data.1
```

## Missing values

Here all missing data get shown in a plot to get an overview of the distribution of them.
Also we can observe how many cantons have how many NAs in relation to...

```{r, MissingValues, echo=FALSE, fig.height = 10, fig.width = 17}
colSums(is.na(data.1)) ##counts all NA in a table
md.pattern(data.1, rotate.names = TRUE) ##shows a table and a plot of the data for the NAs

# data_kanton <- group_by(data, "KT")
# sum(is.na(data_kanton$Fläche))

data.1 %>% count(KT, sort = TRUE) #shows the amount of cantons in dataset per canton

data.1 %>%
  group_by(KT) %>% 
  summarise(non_na_count = sum(is.na(Zimmer))) #Lists all cantons and shows the "NAs"
  
data.1 %>%
     filter(is.na(Zimmer))  %>%
      count(KT) #Shows on the found cantons with NAs

```

## Data Modification

In this step we split the column "PLZ_Ort" which consists a postal code and city name to PLZ and Ort. 

```{r}
data_sep <- data.1$PLZ_Ort%>%
  str_match('(.*\\d) (.*)') %>%
  as_tibble() %>%
  select(2:3) %>%
  set_names(c('PLZ', 'Ort'))
data_sep
```

As this columns are saved separately from the main dataset, we merge it again to the main dataset and remove the old column "PLZ_Ort".

```{r}
data_sort <- data.1%>%select(-PLZ_Ort)
data_clean <- bind_cols(data_sort, data_sep)
data_clean

# data_sort <- data_sort%>%select(-PLZ_Ort)
# data_clean <- bind_cols(data_sort, data_sep)
# data_clean
```

## Add new data set

To also have an overview of the number of residents in the canton, we add a new data set.
We extracted the data set from: <https://www.citypopulation.de/de/switzerland/cities/>

```{r}
#Read new data set and join new data set to our data set.
data_canton <- read_xlsx("SchweizKantone_Einwohner.xlsx", skip = 3)
head(data_canton)
str(data_canton)

#prepare for the join
data_canton <- rename(data_canton, KT = CHE, Kanton = Schweiz, G.Fläche = Gemeindefläche)

data_left_join <- left_join(data_clean, data_canton, by = "KT")
head(data_left_join)
data_left_join
```


# Graphical Analysis

```{r}
head(data_left_join)
str(data_left_join)

```
## Graphical Visualisation

```{r}
plot(y = data_left_join$Miete,
     x = data_left_join$W.Fläche,
     pch = "x",
     title("Price per appartment"),
           xlab = "living space",
           ylab = "rent")
#abline()
```

## Corellation matrix
```{r}
pairs(~Zimmer+Miete+W.Fläche+G.Fläche+Einwohner_2019,data=data_left_join,
      main="Simple Scatterplot")

```


# Analysis

```{r}
data_left_join%>%
top_n(n = 10, wt = Miete)
```

