---
title: "Analysis of Rental Housing Market"
author: 'Fiseha Amine,Martina Schüpbach-Wolf'
date: "02 02 2021"
output:
  pdf_document: default
  html_document: default
always_allow_html: true
---

\newpage 
\tableofcontents
\newpage



#######################
--> Questions:

Am Schluss:
  - Datum am Schluss der Arbeit noch anpassen
  - viele (head) und (str) "unterdrücken / und auch das Zeigen der ganzen Datensätze
  - code der nicht mehr gebraucht wird - löschen
  - alle "labels" benannt? {r}
  
  
- Die Ziele (unten) können wir ja noch anpassen...
- Text "Missing values" unvollständig. Was wollen wir hier genau wissen??? Jenachdem Output anpassen.
      - Dann code anpassen.
      - Tabelle einbauen?
      - Export Bild
      

#######################


# Introduction
This analysis is done as part of the R-Bootcamp module from HS 2020. The aim of the analysis within this scope is to experiment with the different functionalities and methods introduced in this course to answer some analytical and hypothetical research questions.


# Aim of Analysis
Within this work we will analyse the house renting market in Switzerland with the help of open source data from the year 2019. Some of the analysis done in this work are:

1. Analyze the rental price in relation to living space
2. Analyze per canton what types of apartments are mostly available
3. Show where are the most expensive apartments (canton)
4. Show where are the biggest apartments
5. Rental price in relation to size of apartments, number of rooms, population & location

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Libraries
```{r, message=FALSE}
library(readxl)
library(tidyverse)
library(dplyr)
library(mlbench)
library(mice)
library(ggplot2)
library(plotly)
library(shiny)
library(esquisse) 
library(fBasics)
library(lmtest)
```

```{r, special graphical installations}

### needed to export plotly to PDF
#install.packages("webshot")
#webshot::install_phantomjs()

###package for esquisser
#install.packages("esquisse")
```


# Data Import
The data set was downloaded from "Datenportal Schweiz_Wohungsmieten": <https://datenportal.info/wohnungsmarkt/wohnungsmieten/>

It contains the following attributes (in German): 
  ID, Year, Quarter, Apartment type, Room, Area, Rent Gross, Square Meter, Price Gross, Address, Postcode and City, Move-In Date,Building Coordinates, and Canton.

```{r, Data Import}
#Because the data contain "Umlaute" we use "UTF-8" for the read in.
data <- read.csv2("mietinserate_v1.csv", header = TRUE, fileEncoding = "UTF-8")
head(data)
str(data)
summary(data)
```


## Join second data set
To also have an overview of the number of residents in the cantons, we add a new data set.
We extracted the data set from: <https://www.citypopulation.de/de/switzerland/cities/>. It contains the column names: Kanton, KT, Hauptstädte, G.Fläche, Einwohner_1980, Einwohner_1990, Einwohner_2000, Einwohner_2010, and Einwohner_2019.

```{r, Join}
#Read new data set and join new data set to our data set.
data_canton <- read_xlsx("SchweizKantone_Einwohner_org.xlsx", skip = 3)
head(data_canton)
str(data_canton)

#change names of original 4th row (now 1st) of the data set to have those as the column names and for the join preparation
data_canton <- rename(data_canton, Kanton = Schweiz, KT = CHE,  Hauptstädte = Bern, G.Fläche = "41285", Einwohner_1980 = "6365960", Einwohner_1990 = "6873687", Einwohner_2000 = "7288010", Einwohner_2010 = "7870134", Einwohner_2019 = "8603899")

head(data_canton)

#join data sets
data_left_join <- left_join(data, data_canton, by = "KT")
head(data_left_join)

```


# Data Preparation
For the upcoming analysis the data needs to get formatted and cleaned. We transform the data into a data frame. We also transform numeric data into numeric and transform the date data into the correct format. we also rename column names for better readability.

```{r, Data Preparation}

data_2 <- as.data.frame(data_left_join)

#transform data
data_2$Zimmer = as.numeric(data_left_join$Zimmer)
data_2$Fläche = as.numeric(data_left_join$Fläche)
data_2[data_2 == ""] <- NA
data_2$Bezugsdatum =as.Date(data_left_join$Bezugsdatum, "%d.%m.%Y")

#rename data columns for a better readability
data_1 <- rename(data_2, W.Type = Wohnungstyp, Miete = Mietpreis_Brutto, Quad_m = Quadratmeterpreis_Brutto, Bezug = Bezugsdatum, W.Fläche = Fläche)
head(data_1)
```


##Delete Columns

Here we delete columns that are not needed within the scope of this analysis. Those columns appear in the dataset after joining two different datasets in the previous step.

```{r, Delete Columns}

#delete columns that are not needed anymore
data_3 <- data_1 %>% select(-Einwohner_1980, -Einwohner_1990, -Einwohner_2000, -Einwohner_2010)
head(data_3)
```


## Data Modification

In this step we split the column "PLZ_Ort" which consists a postal code and city name to PLZ and Ort. 

```{r, split PLZ_Ort, warning=FALSE}
data_sep <- data_3$PLZ_Ort%>%
  str_match('(.*\\d) (.*)') %>%
  as_tibble() %>%
  select(2:3) %>%
  set_names(c('PLZ', 'Ort'))
head(data_sep)
```


As this columns are saved separately from the main dataset, we merge it again to the main dataset and remove the old column "PLZ_Ort".

```{r, Merge Data set}
data_sort <- data_3%>%select(-PLZ_Ort)
data_clean <- bind_cols(data_sort, data_sep)
head(data_clean)


```


# Graphical Analysis
With the help of graphical visualization we try to see if there are some patterns, outliers, missing values, and if the distribution of the dataset is normal. 


## Missing values

Below a graphical and numerical analysis of all missing data is applied to have an overview of the missing values and their distribution within the dataset. This is necessary to avoid bias in the dataset and have a balanced representation of all cantons equally. For this reason we observe which cantons have how many NAs and if any action (deleting, imputing, replacing, etc.) is needed.

```{r, MissingValuesPlot, eval=FALSE, fig.height = 10, fig.width = 17}
colSums(is.na(data_clean)) ##counts all NAs shown in a table
md.pattern(data_clean, rotate.names = TRUE) ##shows a table and a plot of the data for the NAs
```
The graphical presentation of missing values shows that there is high missing values in number of rooms, square meter of rooms,and entrance date. There is no action which is taken to remove or replace missing values and we will continue our analysis with the missing values included.

```{r, example searches for NAs}
#some example searches for NAs

#data_clean %>%
#  group_by(KT) %>% 
#  summarise(NAs_Zimmer_count = sum(is.na(data_clean$Zimmer))) #Lists all cantons and shows the sum of "NAs" for the column Zimmer including 0"
  
#data_clean %>%
#     filter(is.na(data_clean$Zimmer))%>%
#     count(data_clean$Zimmer) #Lists all cantons including "NAs" for the column "Zimmer" and sums them without including 0
```


## Graphical Visualisation and Analysis

### Corellation matrix

To have a multi-dimensional visualization of several attributes, we visualize a correlation matrix. 

```{r fig.width=9, fig.height=7}
pairs(~Zimmer+Miete+W.Fläche+G.Fläche+Einwohner_2019,data=data_clean,
      main="Correlation Matrix of different attributes")

```
The correlation matrix shows whether there is a correlation among the different factors or not. From the above correlation matrix we can observe that there is a positive correlation between population of a canton and the living area in a commune. 


## 1. Aim: Analysis of rental prices in relation to living space 

Below we visualize the distribution of living area and correlating rental price.

```{r}
plot(y = data_clean$Miete,
     x = data_clean$W.Fläche,
     pch = "x",
     title("Rental Price per Apartment"),
           xlab = "Living Space in square meter",
           ylab = "Rental Price in CHF")

```

The above plot shows that the range of the area of rental apartments lays between 0 and 200 square meter and costs less than 5000 Swiss Francs. There are some outliers with a living area of above 300 and rental price above 10'000 Swiss Francs.


```{r, warning=FALSE}

g <- ggplot(data_clean, aes(x=W.Fläche, y=Miete, xlab = "Rental Price", ylab = "Apartment Area") ) +
  geom_hex(bons = 70) +
  scale_fill_continuous(type = "viridis") +
  theme_bw()

g + ggtitle("Price in Relation to Apartment Area") +
  xlab("Rental Price in CHF") + ylab("Living Space in square meter")
```

The above plot shows the same result as seen with the first plot, however with numerical metric.


## 2. Aim: Analysis of type of apartments that are mostly available (per canton)

### Interactive Graphs

With the help of graphical functions we can produce quality interactive graphs for presentation, reporting, publication, etc. For this purpose we will produce some graphs using "plotly".

```{r}
count_W_Type <- data_clean %>% 
  group_by(KT, W.Type) %>% 
  count(KT, sort = TRUE)

fig <- plot_ly(
  count_W_Type, x = ~KT, y = ~n, type = 'bar', color = ~W.Type)

fig <- fig %>% layout(barmode = "stack",
                      title = 'Apartments per Canton',
                      xaxis = list(title = "Canton"),
                      yaxis = list(title = "Number Apartments"))
                      
fig
```

### Further graphical visualisations for 2. aim

```{r, warning=FALSE}
g <- ggplot(data_clean, aes(x=Miete, y=Zimmer, color=W.Type))+
  geom_point(size=2)
g + ggtitle("Types of Apartments") +
  xlab("Rental Price") + ylab("Rooms")
```

The above plot shows the type of rental housing available for rent colorfully. It shows that most of the rental objects available are apartments (pinc colour).

```{r, warning=FALSE}
##

qplot(y = Zimmer, x = Miete, data = data_clean, facets = ~ W.Type, main = "Types of Apartments", xlab = "Rental Price", ylab = "Rooms")
```

The above graphs shows the same information as above however in a separetely displayed plots. The plot is produced with qplot.

```{r fig.width=9, fig.height=7}
##

boxplot(Zimmer ~ W.Type, data = data_clean, main = "Average number of rooms of the rental objects", xlab = "Type of Apartment", ylab = "Rooms")

```
The above boxplots visualizes the average number of rooms for different types of rental objects. Rental objects of type "Maisonettwohnung" have in average 5 rooms, where as Rental objects of type "Studio" have in average one room.


# Analysis

## 3. Aim: The most expensive apartments

```{r}
top10 <- data_clean%>%top_n(n = 10, wt = Miete)

top10_sorted <- top10[order(top10$Miete, na.last=TRUE) , ]
top10_sorted
```

The most expensive apartment is located in the canton of Zurich and it costs 31'800 Swiss Francs per month. The 10th most expensive apartment costs 10'852 and it is located in the canton of geneve. Here we consider only price, however other factors like apartment area and specific location could be also studied.

### Tabullar presentation of most expensive apartments

Subsetting a dataframe to have a summarized view of the needed factors.

```{r}
data_subset <- top10_sorted %>% select(W.Type,Zimmer, W.Fläche, Miete, Quad_m, KT, Ort)
data_subset
```


## 4. Aim: The biggest apartments

```{r}
top10 <- data_clean%>%top_n(n = 10, wt = W.Fläche)

top10_sorted <- top10[order(top10$W.Fläche, na.last=TRUE) , ]
top10_sorted
```

The biggest apartment available for rental is located in the canton of Graubünden and it has an area of 400 square meter. The 10th biggest Apartment has an area of 350 square meter and it is located in the canton of Zurich. This comparision is however independent of the price, as it varies due to the location of the apartment.


## 5. Rental price in relation to size of apartments, number of rooms, population & location

### Graphical interactive visualization 


```{r, warning=FALSE}

fig2 <- plot_ly(data_clean, y = ~G.Fläche, x = ~Einwohner_2019, type = 'scatter', mode = 'markers', size = 7,
        hoverinfo = 'text',
        text = ~paste('</br> Canton: ', Kanton,
                      '</br> Residents: ', Einwohner_2019,
                      '</br> Community area: ', G.Fläche))

fig2 <- fig2 %>% layout(title = 'Residents in 2019 against community area via canton',
                      xaxis = list(title = "Residents in 2019"),
                      yaxis = list(title = "Community area"))
fig2

tmpFile <- tempfile(fileext = ".png")
export(fig2, file = tmpFile)
```
The above plot shows that the distribution of the population in relation to commune area is normal. Zurich with high population and small communal area and Graubünden with low population and high communal area could be seen as outliers.


### Fitting Linear Model


```{r}
data_scaled <- data_clean %>%          
  mutate_at(c("W.Fläche", "Miete", "Einwohner_2019", "G.Fläche", "Zimmer"), ~(scale(.) %>% as.vector))

simple.fit <- lm(Miete~W.Fläche, data=data_scaled)
summary(simple.fit)

```

The above applied simple regression analysis shows that the rental price varies depending on the apartment area. The adjusted R-squared value is however only 0.43, meaning that only 43% of the data are modeled by the chosen model. 

```{r}
multi.fit = lm(Miete~W.Fläche + G.Fläche + Zimmer + Einwohner_2019, data=data_scaled)
summary(multi.fit)


```

The above multi-regression analysis shows that the price of an apartment is dependent on many factors such as apartment area, population & commune area, but not on the number of rooms. Here, the adjusted R-squared value is better than within the regression analysis with multiple factors is 0.49, meaning that 49% of the data are modeled by the chosen model. To see wether this R-value is good or not, we do residual analysis.

### Residual analysis

To check whether the chosen model represents the dataset well or not we apply residual analysis.

```{r}
#Testing normal distribution and independence assumptions
jarqueberaTest(simple.fit$resid) #Test residuals for normality

dwtest(simple.fit) #Test for independence of residuals

predicted <- predict(simple.fit)
residuals <- residuals(simple.fit)

par(mfrow = c(2, 2))  # Split the plotting panel into a 2 x 2 grid
plot(simple.fit)

```

The residuals analysis above shows that the plot residuals vs. fitted values can be presented in a linear model. Therefore we consider that the chosen "lm" model presents the dataset well. As normality is a precondition for such an anlysis we consider also the Normal Q-Q plot, where the line shows a good fitting with the exception of some data at the end, which we can negelect in this scope.The scale-location plot tests the linear regression assumption of equal variance (homoscedasticity. Meaning that the data is spead equally above and below the line, which is mostly the case in our plot. The residuals vs leverage plot can be used to find influential cases in the dataset, this is however beyond the scope of the analysis.

```{r}
multi.fit = lm(Miete~W.Fläche + G.Fläche + Zimmer + Einwohner_2019, data=data_scaled)
predicted <- predict(multi.fit)
residuals <- residuals(multi.fit)
par(mfrow = c(2, 2))  # Split the plotting panel into a 2 x 2 grid
plot(multi.fit)

```
The above residual analysis for the multi-regression analysis shows also that the residuals and the fitted values can be modeled with a linear model well.As described above, the Norma Q-Q plot shows that there are enough data not fitting the line at the beginning and at the end. precised analysis for normality might be needed, which however will not be done in this scope. The scale-location plot shows that the distribution of the data below and above the line somehow well presented is.


#Chapter of our choice

The "esquisse" package is an interactive "shiny" gadget to create "ggplot2" charts in a browser.
Also the retrieved code from the new plot can get copied out and reused in the further R-code.

```{r, ggplot2 builder package}

if (interactive()) {
# Launch with :
esquisser(data_clean)

#Launch esquisse in browser :
esquisser(data_clean, viewer = "browser")
}
```

As this visualization is done in an external browser, there will not be plots shown in this analytical part.
